Radiance - A Web Application Environment

### 2017-03-15 els2017-radiance/paper.tex
Minor corrections, fixme notes.

\begin{abstract}
  Radiance\cite{radiance} is a set of libraries that provides an environment for web applications. Unlike traditional web frameworks that focus on a set of tools to support the construction and maintenance of a single application, Radiance attempts to allow one to run as many differing applications as desired in the same environment. This goal brings many advantages, as frequently there are common resources in applications that should be shared between them, but cannot, because the applications are separated and developed without regard for sharing. In order to fix this, Radiance provides an extensible interface mechanism to standardise the interaction between users of common resources. To facilitate the separation and encapsulation of the shared URL address space between applications, Radiance also provides a flexible routing mechanism.
\end{abstract}

@@

This separation allows application programmers to model their pages from a perspective that looks much more like the external view. Instead of dealing with named tags, they deal in concrete internal URLs that, in a development setup, often have a relatively direct one-to-one mapping to the external URLs. This makes it easier to visualise and think about the application structure. From the administrator's point of view this setup is more convenient too, as they simply need to think in terms of translations, rather than having to adapt potentially hundreds of different URL tags manually. \\

@@

Ideally, an administrator of a system will not have to touch any source code, and instead will be able to configure the system through a set of human-readable configuration files. It is, of course, still possible to configure the system through usual Lisp code, should one prefer this approach. \\

@@

While Radiance does provide default implementations for all of its interfaces, it is likely that some of them are not usable for a production setting. In order to change, say, the database interface's implementation, we would then have to modify the Radiance core's configuration file. We can either modify the file directly, which can be found through \code{(mconfig-pathname :radiance-core)}, like so:

>>>>

\begin{abstract}
  %% FIXME
  Radiance\cite{radiance} is a set of libraries that provides an environment for web applications. Unlike traditional web frameworks that focus on a set of tools to support the construction and maintenance of a single application, Radiance attempts to allow one to run as many differing applications as desired in the same environment. This goal brings many advantages, as frequently there are common resources in applications that should be shared between them, but cannot, because the applications are separated and developed without regard for sharing. In order to fix this, Radiance provides an extensible interface mechanism to standardise the interaction between users of common resources. To facilitate the separation and encapsulation of the shared URL address space between applications, Radiance also provides a flexible routing mechanism.
\end{abstract}

@@

This separation allows application programmers to model their pages from a perspective that looks much more like the external view. Instead of dealing with named tags, they deal in concrete internal URLs that, in a development setup, often have a relatively direct one-to-one mapping to the external URLs. This makes it easier to visualise and think about the application structure. From the administrator's point of view this setup is more convenient too, as they simply need to think in terms of translations, rather than specific tag instances. \\

@@

%% FIXME
Ideally, an administrator of a system will not have to touch any source code, and instead will be able to configure the system through a set of human-readable configuration files. It is, of course, still possible to configure the system through usual Lisp code, should one prefer this approach. \\

@@

While Radiance does provide default implementations for all of its interfaces, it is likely that some of them are not usable for a production setting. In order to change, say, the database interface's implementation, we would then have to modify the Radiance core's configuration file. We can either modify the file directly like so:
